Optical lattices with low decoherence for ultracold \Li{}

### 2017-01-22 LatticeOptics/latticeOpticsV2.tex
initial

\date{\today}
\begin{abstract}
We describe the design of a stable high power 1064 nm laser for use in optical lattice experiments. The system is based on a high quality mephisto NPRO seeding an array of four heavily modified fiber amplifiers. The intensity of every beam is stabilized with a low noise, nonlinear feedback system, and the waist can be smoothly controlled. 
\end{abstract}
\maketitle
\section{Introduction}
Trapping atoms in an array of optical lattices is a mature and powerful technique for manipulation and control of quantum many-body systems. The use of neutral atoms trapped in an optical lattice has facilitated precision measurements, creation of interesting many body states, and implementation of quantum gates in neutral atoms.

Optical lattices rely on the optical dipole force of light on neutral atoms and the interference of light. Depending on the laser wavelength and the atomic species used, atoms can be drawn toward or repelled by regions of high intensity.

\begin{equation}
    V(\pmb{x}) = \alpha(\omega)|\pmb{E}(\pmb{r})|^2
\end{equation}

When two or more laser beams are interfered, the interference pattern has a spacing $l>\lambda/2$. Different interference geometries provide a wide variety of lattice geometries that have been demonstrated.

By FIGURE - high level block diagram of system
\begin{itemize}
	\item why cold atoms are great, and why you need lattice: clocks, hubbard etc
	\item what are the requirements of lattice
	\item what have we built
\end{itemize}

\section{Measuring Intensity Noise}
\subsection{Photodiodes}
FIGURE: Transimpedance amplifier, with our parameters
\begin{itemize}
	\item Transimpedance amplifier - typical parameters
	\item design criteria, part numbers, typical voltage levels
	\item cutting off windows
	\item thermal stuff (inGas)
	\item lens or no
	\item using photodiodes for looking at these things
\end{itemize}

\subsection{Measuring Power Spectral Density}
FIGURE - maybe WINDOW FUNCTION
\begin{itemize}
\item FFT machine, spectrum analyzer 
window functions revisited, 
-resolution, video bandwidth
\end{itemize}

@@

\section{Fiber Amplifier System}

>>>>

\date{\today}
\begin{abstract}
We describe the design of a stable high power 1064 nm laser for use in optical lattice experiments. The system is based on a high quality mephisto NPRO seeding an array of four heavily modified fiber amplifiers. The intensity of every beam is stabilized with a low noise, nonlinear feedback system, and the waist can be smoothly controlled. 
\end{abstract}
\maketitle
\section{Introduction}
Trapping atoms in an array of optical lattices is a powerful technique for manipulation and control of quantum many-body systems. 
The use of neutral atoms trapped in an optical lattice has facilitated precision measurements, creation of interesting many body states, and implementation of quantum gates in neutral atoms. CITATIONS.
However, a dominant trend in cold atom experiments has been the need to attain colder temperatures at energy scales approaching the Hz level.
Such experiments are limited by heating rates arising from positional, phase and intensity noise of the optical lattice.

By FIGURE - high level block diagram of system

\begin{itemize}
	\item requirements 
	\item what have we built
\end{itemize}

We demonstrate high power lattice

\section{Mephisto}
The lattice laser system is seeded by an Innolight Mephisto laser, which provides approximately 2 W of 1064 nm light. 
This commercial laser utilizes a non-planar ring oscillator (NPRO) design that ensures superb phase and intensity stability. This source is split into four fibers (Thorlabs XXX) by means of polarizing beam splitters. Figure 1 shows the mechanical layout of this system, as well as the intensity noise performance (see supplementary material).

\section{Nufern Fiber Amplifiers}
Quantum gas microscopy of Li requires single site trap frequencies of approximately 1 MHz. 
Such trap frequencies may only be attained using tightly focused high power beams, which requires that the seed power be amplified to approximately 30 W per lattice axis, which is done using

\section{Measuring Intensity Noise}
\subsection{Photodiodes}
FIGURE: Transimpedance amplifier, with our parameters
\begin{itemize}
	\item Transimpedance amplifier - typical parameters
	\item design criteria, part numbers, typical voltage levels
	\item cutting off windows
	\item thermal stuff (inGas)
	\item lens or no
	\item using photodiodes for looking at these thing
\end{itemize}

@@
